Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-06 paper.tex
save

The remaining of this report is structured as follows. In Section~\ref{related-works}, ...

@@

As reviewed in
\citep{smalheiser2009author,ferreira2012brief,levin2012citation}, author
disambiguation algorithms are usually composed of two components: (i) a
similarity function determining whether two publications have been written by a
same author and (ii) a clustering algorithm producing clusters of publications
assumed to be written by a same author. Approaches can be inventorized along
several axes, depending on the type and amount of data available, the way the
similarity function is learned or defined, or the clustering procedure used to
group publications. Methods relying on supervised learning usually make use of
hand-labeled pairs of publications identified as being either from the same or
from different authors for learning automatically a similarity function between
publications \citep{han2004two,huang2006efficient,
culotta2007author,treeratpituk2009disambiguating,tran2014author}. Because
training data is often not easily available, unsupervised approaches propose
instead to use domain-specific similarity functions tailored for author
disambiguation \citep{malin2005unsupervised,mcrae2006also,song2007efficient,
soler2007separating, kang2009co,fan2011graph,schulz2014exploiting}. These later
approaches have the advantage of not requiring  hand-labeled data, but often do
not perform as well as the supervised approaches. To reconcile both worlds,
semi-supervised methods make use of small, manually verified, clusters of
publications and/or of high-precision domain-specific rules to build a training
set of pairs of publications, from which a similarity function is then built
using supervised learning
\citep{ferreira2010effective,torvik2009author,levin2012citation}.
Coincidentally, semi-supervised approaches also allow for the tuning of the
clustering algorithm when the later is applied to a mixed set of labeled
and unlabeled publications, e.g., by maximizing some clustering performance
metric on the known clusters \citep{levin2012citation}.

@@

In this context, we position the work presented in this paper as a
semi-supervised  solution for author disambiguation, but with the significant
advantage of having a very large collection of more than 1 million annotations
of publications known to be from the same author. In particular, the extent and coverage
of this data allows us to revisit, validate and nuance previous findings regarding
supervised learning of similarity functions.

@@

@@

\subsection{Semi-supervised clustering}
% compare agglomerative algorithms
% compare threshold strategies
% compare cold start solutions
% talk about impact of small improvements in terms of citations statistics

>>>>

The remaining of this report is structured as follows. In Section~\ref{related-works},
we first briefly review machine learning solutions for author disambiguation.
The components of our method are then defined in Section~\ref{methods}
and its implementation described in Section~\ref{implementation}. Experiments
are carried out in Section~\ref{experiments}, where we explore and validate
features for the supervised learning of a similarity function and compare
strategies for the semi-supervised clustering of publications.
Finally, conclusions and future works are discussed in Section~\ref{conclusions}.

@@

As reviewed in
\citep{smalheiser2009author,ferreira2012brief,levin2012citation}, author
disambiguation algorithms are usually composed of two main components: (i) a
similarity function determining whether two publications have been written by a
same author and (ii) a clustering algorithm producing clusters of publications
assumed to be written by a same author. Approaches can be inventorized along
several axes, depending on the type and amount of data available, the way the
similarity function is learned or defined, or the clustering procedure used to
group publications. Methods relying on supervised learning usually make use of
hand-labeled pairs of publications identified as being either from the same or
from different authors for learning automatically a similarity function between
publications \citep{han2004two,huang2006efficient,
culotta2007author,treeratpituk2009disambiguating,tran2014author}. Because
training data is often not easily available, unsupervised approaches propose
instead to use domain-specific similarity functions tailored for author
disambiguation \citep{malin2005unsupervised,mcrae2006also,song2007efficient,
soler2007separating, kang2009co,fan2011graph,schulz2014exploiting}. These later
approaches have the advantage of not requiring  hand-labeled data, but often do
not perform as well as the supervised approaches. To reconcile both worlds,
semi-supervised methods make use of small, manually verified, clusters of
publications and/or of high-precision domain-specific rules to build a training
set of pairs of publications, from which a similarity function is then built
using supervised learning
\citep{ferreira2010effective,torvik2009author,levin2012citation}.
Coincidentally, semi-supervised approaches also allow for the tuning of the
clustering algorithm when the later is applied to a mixed set of labeled
and unlabeled publications, e.g., by maximizing some clustering performance
metric on the known clusters \citep{levin2012citation}.

@@

In this context, we position the work presented in this paper as a
semi-supervised  solution for author disambiguation, but with the significant
advantage of having a very large collection of more than 1 million crowdsourced annotations
of publications known to be from the same author. In particular, the extent and coverage
of this data allows us to revisit, validate and nuance previous findings regarding
supervised learning of similarity functions and to better explore strategies
for semi-supervised clustering. Additionally, by releasing the data publicly,
we hope to set a benchmark on further research an author disambiguation
and related topics can  build upon.

@@

\glnote{Figure required here (Eamonn)}

@@

\subsection{Semi-supervised clustering}
% compare agglomerative algorithms
% compare threshold strategies
% compare cold start solutions
